Capstone Movielens Report

### 2025-12-11 reports/capstone-movielens.site/05.appendix.Rmd
Function described: `train_UMGY_SmoothedDay_effect.cv`.

(Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function).

@@

(Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function).

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [loess_de](#func.loess_de) described above);

@@

::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to be used (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$, which controls the degree of smoothing (passed in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above);

@@

::: {.noteblock data-latex=""}
This helper function is also used internally in the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function (described below in section [UMGYDE Model: Regularization] of *this Appendix*) as shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) subsection of *This Function's Description Section* below.
:::

@@

::: {.noteblock data-latex=""}
In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function, along with the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function (both described below in [UMGYDE Model: Regularization] section and this section, respectively).
:::
:::

@@

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_effect](#func.calc_UMGY_effect) functions (both described above in this section).

@@

Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect.cv <- function(lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_SmoothedDay_effect.cv
`lambda` is `NA`")
  }

  calc_day_general_effect.cv(lambda) |> calc_UMGY_effect()  
}
```

>>>>

(Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

@@

(Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

@@

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above;

:::
::: { #func.calc_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [loess_de](#func.loess_de) described above.

@@

::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.

@@

::: {.noteblock data-latex=""}
This function is also called within other helper functions, such as the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) and [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function (described below in sections [UMGYDE Model: Tuning `loess` Params] and [UMGYDE Model: Regularization] of *this Appendix*, respectively). The usage in the latter function is shown in the [Usage](#func.train_UMGY_SmoothedDay_effect.cv.usage) section of *this Description* below.
:::

@@

```{r eval=FALSE}
  train_UMGY_SmoothedDay_effect.cv(best_degree, 
                                   best_span, 
                                   lambda)
```

::: {.noteblock data-latex=""}
In the above code snippet, the `train_UMGY_SmoothedDay_effect.cv` function is called internally from the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) function described below in section [UMGYDE Model: Regularization] of *this Appendix*.
:::
:::

@@

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.degree .sidebar }
  - **degree:** (Integer, $NA$ by default) The degree of the polynomials to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above;

:::
::: { #func.train_UMGY_SmoothedDay_effect.cv.args.span .sidebar }
  - **span:** (Numeric, $NA$ by default ) The parameter $\alpha$ (which controls the degree of smoothing) to pass in the same-named argument to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) described above.

:::
::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Under the hood, this function internally calls the [calc_day_general_effect.cv](#func.calc_day_general_effect.cv) and [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) functions (both described above in this section).

@@

Data frame representing the *UMGYDE Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is non-default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The source code of the [train_UMGY_SmoothedDay_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L113) function is shown below:
```{r eval=FALSE}
train_UMGY_SmoothedDay_effect.cv <- function(degree = NA, 
                                             span = NA,
                                             lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_SmoothedDay_effect.cv
`lambda` is `NA`")
  }

  calc_day_general_effect.cv(lambda) |>
    calc_UMGY_SmoothedDay_effect(degree, span)
}
```
